---
title: "Basic Plots"
author: "Your Name"
date: "`r Sys.Date()`"
output: html_document
---

# Introduction

This document demonstrates basic plotting in R.

```{r pressure-plot, echo=FALSE}
plot(pressure)
```

The plot above shows the relationship between temperature and pressure.

# Conclusion

This is a simple example of an R Markdown document.















---
title: "Basic Plots"
author: "Jeff Goldsmith"
date: 2019-09-10
output: html_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

The purpose of this file is to present a couple of basic plots using `ggplot`.

First we create a dataframe containing variables for our plots.

```{r df_create}
set.seed(1234)

plot_df = tibble(
  x = rnorm(1000, sd = .5),
  y = 1 + 2 * x + rnorm(1000)
)
```

First we show a histogram of the `x` variable.

```{r x_hist}
ggplot(plot_df, aes(x = x)) + geom_histogram()
```

Next we show a scatterplot of `y` vs `x`. 

```{r yx_scatter}
ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```
